Verifying synchronous distributed algorithms using IVy

### 2018-08-12 paper/paper.tex
- page 10, section (IV.i.2): couldn't -> could not

\subsubsection{Cardinality relationships}
There is no cardinality operator in IVy. In set notation we would write something like $|\{n|node(n) \land failed(n)\}|$ to count the number of failed nodes in a system. When programming in a procedural language one would use a loop for this task but, as has been explained in the previous section, loops are somewhat problematic in IVy. The author couldn't find a way to specify an inductive loop invariant for a loop counting the number of failed nodes without a cardinality operator at hand. This means that alternative encodings for the assumption $f<n$ and the \textit{decision condition} ($if\ rounds = f+1$) must be found.

>>>>

\subsubsection{Cardinality relationships}
There is no cardinality operator in IVy. In set notation we would write something like $|\{n|node(n) \land failed(n)\}|$ to count the number of failed nodes in a system. When programming in a procedural language one would use a loop for this task but, as has been explained in the previous section, loops are somewhat problematic in IVy. The author could not find a way to specify an inductive loop invariant for a loop counting the number of failed nodes without a cardinality operator at hand. This means that alternative encodings for the assumption $f<n$ and the \textit{decision condition} ($if\ rounds = f+1$) must be found.
